A large scale study of the languages spoken (by bilinguals) on Mechanical Turk

### 2013-02-17 writeup/paper.tex
Editing Intro.

\section{Overview}
Crowdsourcing has become a key source of data for natural language processing research. Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds a great deal of promise for developing future language technologies. Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data. As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.

>>>>

\section{Overview}
Crowdsourcing has become a key mechanism for collecting data for natural language processing research. Access to a fast, cheap, and flexible workforce has changed the way we collect data, and holds promise for enabling future language technologies. Crowdsourced work has proven effective for collecting massive amounts of simple data annotations, such as annotating data for face recognition software and labeling sentiment in twitter data. As the demands and expectations of automated systems progress, and the complexity of the data required for training increases, however, it becomes natural to ask about the strengths and limitations of the crowd as annotators for natural language data.
